method

### 2022-02-17 06_Paper/ER-ED/method.Rmd

Ratings_view <- data_ER %>%
  subset(data_ER$block == "view_neu" | data_ER$block == "view_neg")
Ratings_view$block <- as.factor(Ratings_view$block)

@@

# Bayes Factors
SubjArousalView_BF <- BayesFactor::anovaBF(formula = arousal ~ block,
                                           data = Ratings_view,
                                           progress = FALSE)
SubjArousalView_con$BF10 <- BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_view$arousal[Ratings_view$block == "view_neu"],
                                                                        y = Ratings_view$arousal[Ratings_view$block == "view_neg"],
                                                                        progress = FALSE, paired = TRUE))$bf

@@

colnames(SubjArousalView_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
# rename contrast for table
SubjArousalView_con[1,1] <- "$View_{negative} - View_{neutral}$"

>>>>

Ratings_view <- data_ER %>%
  subset(data_ER$block == "1_view_neu" | data_ER$block == "2_view_neg")
Ratings_view$block <- as.factor(Ratings_view$block)

@@

# Bayes Factors
SubjArousalView_BF <- BayesFactor::anovaBF(formula = arousal ~ block,
                                           data = Ratings_view,
                                           progress = FALSE)
SubjArousalView_con$BF10 <- BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_view$arousal[Ratings_view$block == "1_view_neu"],
                                                                        y = Ratings_view$arousal[Ratings_view$block == "2_view_neg"],
                                                                        progress = FALSE, paired = TRUE))$bf

@@

colnames(SubjArousalView_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
# rename contrast for table
SubjArousalView_con[1,1] <- "$View_{neutral} - View_{negative}$"
